\mainsection{Experience}

\begin{sidesection}
    \experience
        {Chief Innovation Wizard} % Job title
        {DragonTech} % Organization
        {Fantasy World} % Location
        {2021 - 2024} % Date(s)
        {Development of Magical Data Visualization Tool} % project
        {
        \begin{itemize}
            \item {Led a team of 12 unicorns to create a data visualization tool that predicts the future using magic.}
            \item {Worked closely with wizards to integrate ancient algorithms into modern cloud-based systems.}
            \item {Managed the mystical data lake, ensuring smooth integration of enchanted data sources.}
            \item {Collaborated with the DragonFire team to launch a fire-breathing web application.}
        \end{itemize}
        }
        {Python, Magic, Unicorns, DragonFire, CloudSpells, Quantum Computing, Git, Jupyter}

%---------------------------------------------------------
    \vhrulefill{lightgray}{0.4pt}
    \vspace{1ex}

    \experience
        {Time Travel Engineer} % Job title
        {ChronoCorp} % Organization
        {Time City} % Location
        {2017 - 2020} % Date(s)
        {Building a Time Travel API} % project
        {
        \begin{itemize}
            \item {Developed a fully-functional time travel API, allowing users to visit any point in history.}
            \item {Fixed bugs in the fabric of time, ensuring time loops were properly managed.}
            \item {Built the first-ever Chrono-Database for time-based queries, with full back-up functionality.}
            \item {Worked with the Temporal Engineering team to stabilize time anomalies during deployments.}
            \item {Collaborated with historical figures to ensure that API endpoints were historically accurate.}
        \end{itemize}
        }
        {Time Travel APIs, Quantum Physics, Time-Loop Debugging, JavaScript, Git, Temporal Manipulation}

    \vhrulefill{lightgray}{0.4pt}
    \vspace{2ex}

    \experience
        {Intergalactic Architect}
        {SpaceTech} % Organization
        {Mars} % Location
        {2015 - 2017} % Date(s)
        {Development of Multi-Planetary Communication System} % project
        {
        \begin{itemize}
            \item {Designed and deployed a communication system capable of transmitting data across galaxies.}
            \item {Led a team of Martian engineers to create faster-than-light communication protocols.}
            \item {Developed interplanetary message queues, ensuring secure and instantaneous communication.}
            \item {Worked on alien languages API to allow universal communication between planets.}
            \item {Implemented deep space encryption algorithms to protect transmissions from cosmic threats.}
        \end{itemize}
        }
        {C++, Quantum Networking, Interplanetary APIs, Galactic Databases, Space Encryption, Git, MarsTech}

\end{sidesection}